paper

### 2024-09-19 paper.qmd
.

# Set metadata and formula for LimROTS analysis
meta.info <- "mixing.ratio"
B <- 1000  # Number of bootstrap samples
K <- dim(BM21.Case0)[1]/2 # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "mixing.ratio"
formula.str <- "~ 0 + mixing.ratio"  # Formula for group comparison

@@

@@

# Set metadata and formula for LimROTS analysis
meta.info <- "mixing.ratio"
B <- 1000  # Number of bootstrap samples
K <- dim(BM21.Case1)[1]/2  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30   # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "mixing.ratio"
formula.str <- "~ 0 + mixing.ratio"  # Formula for group comparison

# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = BM21.Case1, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)
```

```{r}
length(which(limrots.result$q_values$qvalues < 0.05))

length(which(limrots.result$FDR < 0.05))

length(which(limrots.result$BH.pvalue < 0.05))

summary(limrots.result$q_values)
plot(limrots.result$q_values)
hist(limrots.result$q_values)
p.value = limrots.result$pvalue
hist(p.value)

library(qvalue)
q <- qvalue(p.value, pi0.method = "bootstrap", lambda  = seq(0.01, 0.95, 0.01))
plot(q)
hist(q)
summary(q)

pi0est(p.value, pi0.method = "bootstrap")

limrots.result.df <- data.frame(row.names  = row.names(limrots.result$data),
                                LimROTS.FC = limrots.result$corrected.logf,
                                FDR = limrots.result$FDR, p.value = limrots.result$pvalue, bh = limrots.result$BH.pvalue)
```

@@

>>>>

# Set metadata and formula for LimROTS analysis
meta.info <- "mixing.ratio"
B <- 1000  # Number of bootstrap samples
K <- dim(BM21.Case0)[1]/4 # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "mixing.ratio"
formula.str <- "~ 0 + mixing.ratio"  # Formula for group comparison

@@

Another feature in LimROTS is the ability to handle more than two groups using moderated F-statistics and ROTS optimization. In this example, three different ratio mixtures were extracted from the BM21 dataset and processed similarly to the dataset in case study 3. Therefore, we expect to see the maximum number of features that are significantly different with a true effect.

@@

# Set metadata and formula for LimROTS analysis
meta.info <- "mixing.ratio"
B <- 1000  # Number of bootstrap samples
K <- dim(BM21.Case1)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30   # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "mixing.ratio"
formula.str <- "~ 0 + mixing.ratio"  # Formula for group comparison

# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = BM21.Case1, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)

saveRDS(limrots.result , "paperdata/BM21.Case1.limrots.rds")
```

@@

## BM21 Case study 5
